One exact and one random sampling method to assess the reliability of inferences from network enrichment analysis

### 2018-05-07 doc/genesetdp.tex
description of normalized rank.

\begin{figure}[htb]
  \begin{center}
      \includegraphics[width=1.0\textwidth]{figures/calibration_multiple.png}
  \end{center}
  \caption{{\bf Calibration of GeneSetDP and GeneSetMC.} We selected 10000 random sets of 10, 20 and 30 genes from the investigated genome definition and calculated their $p$ values with GeneSetMC and GeneSetDP against the ``Glycolysis/Gluconeogenesis'' pathway. To test the $p$~values uniformity we plotted them against their normalized rank. We also added the calibration curve of BinoX, evaluated on the same random sets.}
  \label{fig:calibration}
\end{figure}

>>>>

\begin{figure}[htb]
  \begin{center}
      \includegraphics[width=1.0\textwidth]{figures/calibration_multiple.png}
	  % \includegraphics{figures/calibration_legend.png}
  \end{center}
  \caption{{\bf Calibration of GeneSetDP and GeneSetMC.} We selected 10000 random sets of 10, 20 and 30 genes from the investigated genome definition and calculated their $p$ values with GeneSetMC and GeneSetDP against the ``Glycolysis/Gluconeogenesis'' pathway. To test the $p$~values uniformity we plotted them against their normalized rank, i.e. each $p$~value's (<rank>-0.5)/<total number of $p$~values>). We also added the calibration curve of BinoX, evaluated on the same random sets. The dashed line shows $y = x$ and the dotted lines $y = 2x$ and $y = 0.5x$}
  \label{fig:calibration}
\end{figure}
